Replication of Gantman et al. 2024

### 2024-03-15 manuscript.qmd
first draft of a complete analysis

This is a replication of the study by Gantman et al. (2014). Replications are important for *reasons*.

@@

`r n_subjects` subjects were recruited for the study. After applying the exclusion criteria, `r n_subjects_remaining` subjects remain. `r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.

@@

```{r}
#| label: fig-beh-pop-out
#| fig-cap: Accuracy for word trials in the fashion and moral conditions showed that performance was much higher than expected. We later discovered this was due to a difference in procedure between our study and the original study.

@@

ggplot(behavioral_pop_out_data, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
  geom_point()+
  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), size=0.25)+
  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), size=0.25, alpha=0.3)+
  labs(x="Accuracy for non-category words", y="Accuracy for category words")+
  facet_grid(.~category, labeller = as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words")))+ 
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  coord_cartesian(xlim=c(0.5,1), ylim=c(0.5,1))+
  theme_bw(base_size=12)+
  theme(aspect.ratio=1, panel.grid=element_blank())
```

@@

coefficient_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Estimate']
coefficient_moral_pop_out_se <- behavioral_model_moral_pop_out$coefficients[2, 'Robust S.E.']
z_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Robust z']
p_moral_pop_out <- z_moral_pop_out %>% pnorm(lower.tail = FALSE)

@@

coefficient_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Estimate']
coefficient_fashion_pop_out_se <- fashion_model_moral_pop_out$coefficients[2, 'Robust S.E.']
z_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Robust z']
p_fashion_pop_out <- z_fashion_pop_out %>% pnorm(lower.tail = FALSE)
```

Accuracy for moral words was not significantly different between category and non-category words, $b = `r coefficient_moral_pop_out`$, $SE = `r coefficient_moral_pop_out_se`$, $z = `r z_moral_pop_out`$, $p = `r p_moral_pop_out`$. Accuracy for fashion words was significantly different between category and non-category words, $b = `r coefficient_fashion_pop_out`$, $SE = `r coefficient_fashion_pop_out_se`$, $z = `r z_fashion_pop_out`$, $p = `r p_fashion_pop_out`$.

```{r}
#| label: Compute response time differences for words
#| include: false

subject_level_rt <- behavioral_data_test_set %>%
  filter(correct == TRUE) %>%
  group_by(subject_id, word_category, category, is_word) %>%
  summarize(rt = mean(rt, na.rm = TRUE))
```

```{r}
#| include: false

behavioral_pop_out_data <- subject_level_rt %>%
  filter(is_word == TRUE)

ggplot(behavioral_pop_out_data, aes(x=word_category, y=rt, group=subject_id))+
  geom_point()+
  geom_line()+
  #labs(x="Word Type", y="Accuracy")+
  facet_grid(.~category)+
  theme_bw()
```

```{r}
#| include: false

m <- gee(rt ~ word_category,
    id = subject_id,
    subset = is_word == TRUE & correct == TRUE & category == "moral",
    data = behavioral_data_test_set,
    family = gaussian,
    corstr = "exchangeable")

summary(m)
```

@@

```{r}
grand_average <- subject_eeg %>%
  group_by(t, electrode, word_category, category, is_word) %>%
  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
```

```{r}
#| label: fig-grand-averages
#| fig-width: 10
#| fig-height: 8
ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  facet_grid(electrode~category)+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal()+
  theme(panel.grid = element_blank())
```

```{r}
#| label: Count the number of good segments per subject
#| include: false
count_good_trials <- eeg_data %>%
  filter(t==0, electrode=="Cz") %>%
  group_by(subject) %>%
  summarize(n=n()) %>%
  mutate(percent = (n/600)*100)

@@

```{r}
```

@@

@@

p2_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p2" & category == "fashion" & is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model$coefficients

n2_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "n2" & category == "fashion"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model$coefficients

p3_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p3" & category == "fashion"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model$coefficients

lpp_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "lpp" & category == "fashion"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model$coefficients
```
```{r}
#| label: Run GEE models for all time windows, moral data pop-out
#| include: false

p2_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model$coefficients

n2_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model$coefficients

p3_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model$coefficients

lpp_model <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model$coefficients
```

p2_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p2" & category == "moral",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model$coefficients

n2_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "n2" & category == "moral",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model$coefficients

p3_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p3" & category == "moral",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model$coefficients

lpp_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "lpp" & category == "moral",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model$coefficients

@@

p2_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p2" & category == "fashion",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model$coefficients

n2_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "n2" & category == "fashion",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model$coefficients

p3_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p3" & category == "fashion",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model$coefficients

lpp_model <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "lpp" & category == "fashion",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model$coefficients

>>>>

This is a replication of the study by Gantman et al. (2020). Replications are important for *reasons*.

@@

`r n_subjects` subjects participated in the study. After applying the exclusion criteria, `r n_subjects_remaining` subjects remain. `r length(exclude_for_fashion_twice_subjects)` subjects were excluded for receiving fashion words twice due to a technical error, `r length(exclude_for_non_response_subjects)` subjects were excluded for having a non-response rate greater than 50%, and `r length(exclude_for_non_word_response_subjects)` subjects were excluded for having a non-word response rate greater than 90%.

@@

```{r}
#| label: fig-beh-pop-out
#| fig-cap: Performance for in-category words and out-of-category words for each participant. Points above the diagonal represent higher accuracy for in-category words. Overall accuracy was much higher than expected. We later discovered this was due to a difference in procedure between our study and the original study. Lines represent +/- 1 SE.
#| echo: false

@@

ggplot(behavioral_pop_out_data, aes(x=`accuracy_non-category`, y=`accuracy_category`))+
  geom_point()+
  geom_linerange(aes(ymin=`accuracy_category`-`se_category`, ymax=`accuracy_category`+`se_category`), linewidth=0.25)+
  geom_linerange(aes(xmin=`accuracy_non-category`-`se_non-category`, xmax=`accuracy_non-category`+`se_non-category`), linewidth=0.25, alpha=0.3)+
  labs(x="Accuracy for non-category words", y="Accuracy for category words")+
  facet_grid(.~category, labeller = as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words")))+ 
  geom_abline(intercept = 0, slope = 1, linetype="dashed")+
  coord_cartesian(xlim=c(0.5,1), ylim=c(0.5,1))+
  theme_bw(base_size=12)+
  theme(aspect.ratio=1, panel.grid=element_blank())
```

@@

coefficient_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Estimate']
coefficient_moral_pop_out_se <- behavioral_model_moral_pop_out$coefficients[2, 'Robust S.E.']
z_moral_pop_out <- behavioral_model_moral_pop_out$coefficients[2, 'Robust z']
p_moral_pop_out <- (1 - pnorm(abs(z_moral_pop_out))) * 2

@@

coefficient_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Estimate']
coefficient_fashion_pop_out_se <- fashion_model_moral_pop_out$coefficients[2, 'Robust S.E.']
z_fashion_pop_out <- fashion_model_moral_pop_out$coefficients[2, 'Robust z']
p_fashion_pop_out <- (1 - pnorm(abs(z_fashion_pop_out))) * 2

mean_moral_in_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "moral" & word_category == "category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_moral_out_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "moral" & word_category == "non-category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_fashion_in_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "fashion" & word_category == "category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100

mean_fashion_out_category <- subject_level_accuracy %>%
  filter(is_word == TRUE & category == "fashion" & word_category == "non-category") %>%
  pull(accuracy) %>%
  mean() %>% 
  round(4)* 100
```

We found a pop-out effect for both moral and fashion words. In the moral condition, participants were `r mean_moral_in_category`% accurate for moral words and `r mean_moral_out_category`% accurate for non-moral words. This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_moral_pop_out %>% round(3)`, *SE* = `r coefficient_moral_pop_out_se %>% round(3)`, *z* = `r z_moral_pop_out %>% round(3)`, *p* = `r p_moral_pop_out %>% format(scientific=FALSE)`.

In the fashion condition, participants were `r mean_fashion_in_category`% accurate for fashion words and `r mean_fashion_out_category`% accurate for non-fashion words.  This difference was statistically significant in the GEE model, $\beta$ = `r coefficient_fashion_pop_out`, *SE* = `r coefficient_fashion_pop_out_se %>% round(3)`, *z* = `r z_fashion_pop_out %>% round(3)`, *p* = `r p_fashion_pop_out %>% format(scientific=FALSE)`.

@@

```{r}
#| label: Grand average computation
#| include: false

grand_average <- subject_eeg %>%
  group_by(t, electrode, word_category, category, is_word) %>%
  summarize(M = mean(v), SE = sd(v)/sqrt(n()))
```

```{r}
#| label: fig-grand-averages
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Grand average waveforms. Shaded areas represent +/- 1 SE.
#| echo: false

ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  scale_color_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_fill_brewer(palette="Set1", name="Is word?", labels=c("Non-word", "Word"))+
  scale_linetype_manual(name="Word Category", labels=c("Moral/Fashion", "Non-Moral/Non-Fashion"), values=c("solid", "dashed"))+
  facet_grid(electrode~category, labeller=as_labeller(c("fashion"="Fashion Words", "moral"="Moral Words", "Cz"="Cz", "Pz"="Pz" )))+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal(base_size=12)+
  theme(panel.grid = element_blank())
```

```{r}
#| label: Count the number of good segments per subject
#| include: false

count_good_trials <- eeg_data %>%
  filter(t==0, electrode=="Cz") %>%
  group_by(subject) %>%
  summarize(n=n()) %>%
  mutate(percent = (n/600)*100)

@@

@@

### Words vs. Non-Words

Following Gantman and Van Bavel, we looked for word vs. non-word ERP effects at each time window at electrode Pz.

p2_model_moral_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p2" & category == "moral" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model_moral_word_nonword_beta <- p2_model_moral_word_nonword$coefficients[2, 'Estimate']
p2_model_moral_word_nonword_se <- p2_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
p2_model_moral_word_nonword_z <- p2_model_moral_word_nonword$coefficients[2, 'Robust z']
p2_model_moral_word_nonword_p <- (1 - pnorm(abs(p2_model_moral_word_nonword_z))) * 2

n2_model_moral_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "n2" & category == "moral" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model_moral_word_nonword_beta <- n2_model_moral_word_nonword$coefficients[2, 'Estimate']
n2_model_moral_word_nonword_se <- n2_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
n2_model_moral_word_nonword_z <- n2_model_moral_word_nonword$coefficients[2, 'Robust z']
n2_model_moral_word_nonword_p <- (1 - pnorm(abs(n2_model_moral_word_nonword_z))) * 2

p3_model_moral_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p3" & category == "moral" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model_moral_word_nonword_beta <- p3_model_moral_word_nonword$coefficients[2, 'Estimate']
p3_model_moral_word_nonword_se <- p3_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
p3_model_moral_word_nonword_z <- p3_model_moral_word_nonword$coefficients[2, 'Robust z']
p3_model_moral_word_nonword_p <- (1 - pnorm(abs(p3_model_moral_word_nonword_z))) * 2

lpp_model_moral_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "lpp" & category == "moral" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model_moral_word_nonword_beta <- lpp_model_moral_word_nonword$coefficients[2, 'Estimate']
lpp_model_moral_word_nonword_se <- lpp_model_moral_word_nonword$coefficients[2, 'Robust S.E.']
lpp_model_moral_word_nonword_z <- lpp_model_moral_word_nonword$coefficients[2, 'Robust z']
lpp_model_moral_word_nonword_p <- (1 - pnorm(abs(lpp_model_moral_word_nonword_z))) * 2
```

In the moral condition, words elicited a more positive ERP in the P2 window ($\beta$ = `r p2_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r p2_model_moral_word_nonword_se %>% round(3)`, *z* = `r p2_model_moral_word_nonword_z %>% round(3)`, *p* = `r p2_model_moral_word_nonword_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r n2_model_moral_word_nonword_se %>% round(3)`, *z* = `r n2_model_moral_word_nonword_z %>% round(3)`, *p* = `r n2_model_moral_word_nonword_p %>% format(scientific=FALSE)`), and P3 window ($\beta$ = `r p3_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r p3_model_moral_word_nonword_se %>% round(3)`, *z* = `r p3_model_moral_word_nonword_z %>% round(3)`, *p* = `r p3_model_moral_word_nonword_p %>% format(scientific=FALSE)`). There was no significant effect in the LPP window ($\beta$ = `r lpp_model_moral_word_nonword_beta %>% round(3)`, *SE* = `r lpp_model_moral_word_nonword_se %>% round(3)`, *z* = `r lpp_model_moral_word_nonword_z %>% round(3)`, *p* = `r lpp_model_moral_word_nonword_p %>% format(scientific=FALSE)`).

p2_model_fashion_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p2" & category == "fashion" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model_fashion_word_nonword_beta <- p2_model_fashion_word_nonword$coefficients[2, 'Estimate']
p2_model_fashion_word_nonword_se <- p2_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
p2_model_fashion_word_nonword_z <- p2_model_fashion_word_nonword$coefficients[2, 'Robust z']
p2_model_fashion_word_nonword_p <- (1 - pnorm(abs(p2_model_fashion_word_nonword_z))) * 2

n2_model_fashion_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "n2" & category == "fashion" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model_fashion_word_nonword_beta <- n2_model_fashion_word_nonword$coefficients[2, 'Estimate']
n2_model_fashion_word_nonword_se <- n2_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
n2_model_fashion_word_nonword_z <- n2_model_fashion_word_nonword$coefficients[2, 'Robust z']
n2_model_fashion_word_nonword_p <- (1 - pnorm(abs(n2_model_fashion_word_nonword_z))) * 2

p3_model_fashion_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "p3" & category == "fashion" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model_fashion_word_nonword_beta <- p3_model_fashion_word_nonword$coefficients[2, 'Estimate']
p3_model_fashion_word_nonword_se <- p3_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
p3_model_fashion_word_nonword_z <- p3_model_fashion_word_nonword$coefficients[2, 'Robust z']
p3_model_fashion_word_nonword_p <- (1 - pnorm(abs(p3_model_fashion_word_nonword_z))) * 2

lpp_model_fashion_word_nonword <- gee(v ~ is_word,
    id = subject,
    subset = erp_component == "lpp" & category == "fashion" & electrode == "Pz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model_fashion_word_nonword_beta <- lpp_model_fashion_word_nonword$coefficients[2, 'Estimate']
lpp_model_fashion_word_nonword_se <- lpp_model_fashion_word_nonword$coefficients[2, 'Robust S.E.']
lpp_model_fashion_word_nonword_z <- lpp_model_fashion_word_nonword$coefficients[2, 'Robust z']
lpp_model_fashion_word_nonword_p <- (1 - pnorm(abs(lpp_model_fashion_word_nonword_z))) * 2

In the fashion condition, words elicited a more positive ERP only in the P2 window ($\beta$ = `r p2_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r p2_model_fashion_word_nonword_se %>% round(3)`, *z* = `r p2_model_fashion_word_nonword_z %>% round(3)`, *p* = `r p2_model_fashion_word_nonword_p %>% format(scientific=FALSE)`). There was no significant difference in the N2 window ($\beta$ = `r n2_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r n2_model_fashion_word_nonword_se %>% round(3)`, *z* = `r n2_model_fashion_word_nonword_z %>% round(3)`, *p* = `r n2_model_fashion_word_nonword_p %>% format(scientific=FALSE)`), P3 window ($\beta$ = `r p3_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r p3_model_fashion_word_nonword_se %>% round(3)`, *z* = `r p3_model_fashion_word_nonword_z %>% round(3)`, *p* = `r p3_model_fashion_word_nonword_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_word_nonword_beta %>% round(3)`, *SE* = `r lpp_model_fashion_word_nonword_se %>% round(3)`, *z* = `r lpp_model_fashion_word_nonword_z %>% round(3)`, *p* = `r lpp_model_fashion_word_nonword_p %>% format(scientific=FALSE)`).

### Pop-out effects

Also following Gantman and Van Bavel, we looked for ERP differences related to the category vs. non-category distinction in all four time windows at electrode Cz.

```{r}
#| label: Run GEE models for all time windows, moral data pop-out
#| include: false

p2_model_moral_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p2" & category == "moral" & is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model_moral_popout_beta <- p2_model_moral_popout$coefficients[2, 'Estimate']
p2_model_moral_popout_se <- p2_model_moral_popout$coefficients[2, 'Robust S.E.']
p2_model_moral_popout_z <- p2_model_moral_popout$coefficients[2, 'Robust z']
p2_model_moral_popout_p <- (1 - pnorm(abs(p2_model_moral_popout_z))) * 2

n2_model_moral_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "n2" & category == "moral" & is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model_moral_popout_beta <- n2_model_moral_popout$coefficients[2, 'Estimate']
n2_model_moral_popout_se <- n2_model_moral_popout$coefficients[2, 'Robust S.E.']
n2_model_moral_popout_z <- n2_model_moral_popout$coefficients[2, 'Robust z']
n2_model_moral_popout_p <- (1 - pnorm(abs(n2_model_moral_popout_z))) * 2

p3_model_moral_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p3" & category == "moral"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model_moral_popout_beta <- p3_model_moral_popout$coefficients[2, 'Estimate']
p3_model_moral_popout_se <- p3_model_moral_popout$coefficients[2, 'Robust S.E.']
p3_model_moral_popout_z <- p3_model_moral_popout$coefficients[2, 'Robust z']
p3_model_moral_popout_p <- (1 - pnorm(abs(p3_model_moral_popout_z))) * 2

lpp_model_moral_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "lpp" & category == "moral"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model_moral_popout_beta <- lpp_model_moral_popout$coefficients[2, 'Estimate']
lpp_model_moral_popout_se <- lpp_model_moral_popout$coefficients[2, 'Robust S.E.']
lpp_model_moral_popout_z <- lpp_model_moral_popout$coefficients[2, 'Robust z']
lpp_model_moral_popout_p <- (1 - pnorm(abs(lpp_model_moral_popout_z))) * 2

In the moral condition, there was a significant difference between moral and non-moral words in the P2 window ($\beta$ = `r p2_model_moral_popout_beta %>% round(3)`, *SE* = `r p2_model_moral_popout_se %>% round(3)`, *z* = `r p2_model_moral_popout_z %>% round(3)`, *p* = `r p2_model_moral_popout_p %>% format(scientific=FALSE)`) and the LPP window ($\beta$ = `r lpp_model_moral_popout_beta %>% round(3)`, *SE* = `r lpp_model_moral_popout_se %>% round(3)`, *z* = `r lpp_model_moral_popout_z %>% round(3)`, *p* = `r lpp_model_moral_popout_p %>% format(scientific=FALSE)`). However, in both of these cases the effect was in the *opposite* direction as the original, with non-moral words having a more positive ERP. There was no significant difference between moral and non-moral words in the N2 window ($\beta$ = `r n2_model_moral_popout_beta %>% round(3)`, *SE* = `r n2_model_moral_popout_se %>% round(3)`, *z* = `r n2_model_moral_popout_z %>% round(3)`, *p* = `r n2_model_moral_popout_p %>% format(scientific=FALSE)`) and P3 window ($\beta$ = `r p3_model_moral_popout_beta %>% round(3)`, *SE* = `r p3_model_moral_popout_se %>% round(3)`, *z* = `r p3_model_moral_popout_z %>% round(3)`, *p* = `r p3_model_moral_popout_p %>% format(scientific=FALSE)`).

@@

p2_model_fashion_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p2" & category == "fashion" & is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p2_model_fashion_popout_beta <- p2_model_fashion_popout$coefficients[2, 'Estimate']
p2_model_fashion_popout_se <- p2_model_fashion_popout$coefficients[2, 'Robust S.E.']
p2_model_fashion_popout_z <- p2_model_fashion_popout$coefficients[2, 'Robust z']
p2_model_fashion_popout_p <- (1 - pnorm(abs(p2_model_fashion_popout_z))) * 2

n2_model_fashion_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "n2" & category == "fashion"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

n2_model_fashion_popout_beta <- n2_model_fashion_popout$coefficients[2, 'Estimate']
n2_model_fashion_popout_se <- n2_model_fashion_popout$coefficients[2, 'Robust S.E.']
n2_model_fashion_popout_z <- n2_model_fashion_popout$coefficients[2, 'Robust z']
n2_model_fashion_popout_p <- (1 - pnorm(abs(n2_model_fashion_popout_z))) * 2

p3_model_fashion_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "p3" & category == "fashion"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

p3_model_fashion_popout_beta <- p3_model_fashion_popout$coefficients[2, 'Estimate']
p3_model_fashion_popout_se <- p3_model_fashion_popout$coefficients[2, 'Robust S.E.']
p3_model_fashion_popout_z <- p3_model_fashion_popout$coefficients[2, 'Robust z']
p3_model_fashion_popout_p <- (1 - pnorm(abs(p3_model_fashion_popout_z))) * 2

lpp_model_fashion_popout <- gee(v ~ word_category,
    id = subject,
    subset = erp_component == "lpp" & category == "fashion"& is_word == TRUE & electrode == "Cz",
    data = time_window_data,
    family = gaussian,
    corstr = "exchangeable") %>% summary()

lpp_model_fashion_popout_beta <- lpp_model_fashion_popout$coefficients[2, 'Estimate']
lpp_model_fashion_popout_se <- lpp_model_fashion_popout$coefficients[2, 'Robust S.E.']
lpp_model_fashion_popout_z <- lpp_model_fashion_popout$coefficients[2, 'Robust z']
lpp_model_fashion_popout_p <- (1 - pnorm(abs(lpp_model_fashion_popout_z))) * 2

@@

In the fashion condition, there was a significant difference in the ERP for fashion and non-fashion words in the effect in the P3 window ($\beta$ = `r p3_model_fashion_popout_beta %>% round(3)`, *SE* = `r p3_model_fashion_popout_se %>% round(3)`, *z* = `r p3_model_fashion_popout_z %>% round(3)`, *p* = `r p3_model_fashion_popout_p %>% format(scientific=FALSE)`). There was no significant difference in the P2 window, ($\beta$ = `r p2_model_fashion_popout_beta %>% round(3)`, *SE* = `r p2_model_fashion_popout_se %>% round(3)`, *z* = `r p2_model_fashion_popout_z %>% round(3)`, *p* = `r p2_model_fashion_popout_p %>% format(scientific=FALSE)`), N2 window ($\beta$ = `r n2_model_fashion_popout_beta %>% round(3)`, *SE* = `r n2_model_fashion_popout_se %>% round(3)`, *z* = `r n2_model_fashion_popout_z %>% round(3)`, *p* = `r n2_model_fashion_popout_p %>% format(scientific=FALSE)`), and LPP window ($\beta$ = `r lpp_model_fashion_popout_beta %>% round(3)`, *SE* = `r lpp_model_fashion_popout_se %>% round(3)`, *z* = `r lpp_model_fashion_popout_z %>% round(3)`, *p* = `r lpp_model_fashion_popout_p %>% format(scientific=FALSE)`).
